Python as a machine learning language: experiences from the \textit{scikit-learn} project

### 2013-06-05 paper.tex
Some rewordings

\begin{abstract}
The \textit{scikit-learn} project is an increasingly popular open source machine
learning library designed to be simple and efficient, accessible to non-experts,
and reusable in various contexts. In this paper, we present and discuss our
design choices for the application programming interface (API) of the project.
In particular, we describe the \textit{estimator} interface shared by all
learning and processing units in the library and then discuss its advantages in
terms of composition and reusability. The paper also comments on implementation
details specific to the Python ecosystem and highlights obstacles faced by users
and developers of machine learning algorithms.
\end{abstract}

@@

The \textit{scikit-learn} project~\citep{pedregosa2011} is an open source
machine learning library for the Python programming language. The ambition of
the project is to provide  effective and long-established machine learning tools
within a programming environment that is easy-to-use, efficient, accessible to
non-machine learning experts and reusable in various scientific areas. In
itself, the project is a library of machine learning tools including, among
others, learning algorithms, model selection tools and preprocessing procedures
rather than a novel domain-specific programming language. From its core, the
library has been designed to tie in with the set of numeric and scientific
packages centered around the Numpy and SciPy~\citep{vanderwalt2011,
varoquaux2013scipy} libraries. As such, \textit {scikit-learn} is intended to be
used within Python scripts and requires some Python programming knowledge. At
the time, it offers no command line or graphical user interface.

Started in 2009, \textit{scikit-learn} counts a large team of volunteer
international developers mainly consisting of scientists and researchers from
various areas (e.g., machine learning, natural language processing or
neuroscience). The project also greatly benefits from many occasional
contributors proposing small code and/or documentation fixes or improvements.
Because of this large base of developers, important efforts are demanded to make
the project maintainable. In particular, we emphasize on high-quality and well-documented
code  in order to ease future developments by external contributors.
\textcolor{red}{TODO: Mention some good coding practices (automatic testing, code
reviews, etc)}

Within the past few years, the project has proven to be valuable to an  ever-
increasing user base. Its popularity can be gauged from various indicators,
including hundreds of citations in scientific papers, successes in various
machine learning challenges, or statistics\footnote{\textcolor{red}{Cite some
statistics here.}} from our repositories and mailing lists.

>>>>

\begin{abstract}
The \textit{scikit-learn} project is an increasingly popular open source machine
learning library designed to be simple and efficient, accessible to non-experts,
and reusable in various contexts. In this paper, we present and discuss our
design choices for the application programming interface (API) of the project.
In particular, we describe our core \textit{estimator} interface shared by all
learning and processing units in the library and then discuss its advantages in
terms of composition and reusability. The paper also comments on implementation
details specific to the Python ecosystem and highlights obstacles faced by users
and developers of the library.
\end{abstract}

@@

The \textit{scikit-learn} project~\citep{pedregosa2011} is an open source
machine learning library for the Python programming language. The ambition of
the project is to provide  effective and long-established machine learning tools
within a programming environment that is easy-to-use, efficient, accessible to
non-machine learning experts and reusable in various scientific areas. In
itself, the project is a library of machine learning tools including, among
others, learning algorithms, model selection tools and preprocessing procedures
rather than being a novel domain-specific programming language. From its core,
the library has been designed to tie in with the set of numeric and scientific
packages centered around the Numpy and SciPy~\citep{vanderwalt2011,
varoquaux2013scipy} libraries. As such, \textit {scikit-learn} is intended to be
used within Python scripts and requires some Python programming knowledge. At
the time, it offers no command line or graphical user interface.

Started in 2009, \textit{scikit-learn} counts a large team of volunteer
international developers mainly consisting of scientists and researchers from
various fields (e.g., machine learning, natural language processing or
neuroscience). The project also greatly benefits from many occasional
contributors proposing small code and/or documentation fixes or improvements.
Because of this large base of developers, important efforts are deployed to make
the project maintainable. In particular, we emphasize on high-quality and well-documented
code  in order to ease future developments by external contributors.
\textcolor{red}{TODO: Mention some good coding practices (automatic testing, code
reviews, etc)}

Within the past few years, the project has proven to be valuable to an  ever
increasing user base. Its popularity can be gauged from various indicators,
including hundreds of citations in scientific papers, successes in various
machine learning challenges, or significant statistics\footnote{\textcolor{red}{Cite some
statistics here.}} derived from our repositories and mailing lists.
